A large leading tail of atmospheric escape in the HAT-P-67 b system

### 2023-02-16 paper/paper1/ms.tex
Thinking about vsini and planet motion
some tiny prose

\begin{figure}
    \includegraphics[width=\linewidth]{figures/best_fit_orbit.png}
    \caption{Best fit orbit overlaid on the composite TESS lightcurve.  The 1 ppt TESS precision improves upon the ground-based detection and refining the orbital properties and ephemerides.}
    \label{fig:transit}
\end{figure}

@@

@@

\subsection{Keck HIRES}
We retrieved 22 epochs of archival \emph{Keck HIRES} spectra via the Keck Observatory Archive (KOA). Of these, 19 were acquired through the iodine cell as reported by \citet{2017AJ....153..211Z}, providing RV orbit constraints.  The 14\arcsec~ slit height of the C2 decker appears to cause order overlap in \ion{Ca}{2} H and K lines, which contaminated the spectral extraction for 14 of the 22 spectra.  The 3\farcs5 B2 decker allowed the faithful extraction of this region for 6 spectra.  The

>>>>

@@

\begin{figure}
    \includegraphics[width=\linewidth]{figures/best_fit_orbit.png}
    \caption{Best fit orbit overlaid on the composite TESS lightcurve.}
    \label{fig:transit}
\end{figure}

@@

\subsection{Keck HIRES}
We retrieved 22 epochs of archival \emph{Keck HIRES} spectra via the Keck Observatory Archive (KOA). Of these, 19 were acquired through the iodine cell as reported by \citet{2017AJ....153..211Z}, providing RV orbit constraints.  The 14\arcsec~ slit height of the C2 decker appears to cause order overlap in \ion{Ca}{2} H and K lines, which contaminated the spectral extraction for 14 of the 22 spectra.  The 3\farcs5 B2 decker allowed the faithful extraction of this region for 6 spectra, which exhibit no perceptible \ion{Ca}{2} H and K variability.  The H~$\alpha$ region similarly exhibited no perceptible variability.  The timing of these spectra coincidentally missed the orbital phases ($-0.3$ to $+0.03$) where we see the greatest \ion{He}{1} 10833 \AA~ absorption excess, leaving open the possibility that detectable H~$\alpha$ absorption could be present at more favorable orbital phases.  New spectra or a more careful extraction of the archival C2 decker spectra would be needed.
